DP Problems of Interest

### 2012-10-15 docs/roadmap/problems.tex
Initial, although probably bugged matrix multiplication CPU algorithm.

\item Optimizations:\ul
	\item {\color{red}We need to swap vertically the matrix to have a normalized progression towards bottom right. To do that, we need to map all indices $i \mapsto n-1-i$, but since we want to store the matrix sparsely, we might want to transform it into a lower triangular matrix as we can provide a size-independent mapping of element indices.
	XXX: what's the best trade off ? progress towards bottom right VS map indices more efficiently ? Also consider efficient memory usage$\to$ larger problem VS standardized layout}
	\ule
\ole

>>>>

\item Optimizations:\ul
	\item We need to swap vertically the matrix to have a normalized progression towards bottom right. To do that, we need to map all indices $i \mapsto n-1-i$ and we obtain a new recurrence relation:
	\[M_{(i,j)}=\min_{i\le k<j}\left\{\begin{array}{l} M_{(i,k)}+M_{(2i-1 -k,j)}+r_i \cdot c_k \cdot c_j \end{array}\right. \]
	With the initialization at $M_{(i,n-i-1)}$
	\ule
\ole
